Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-15 ms.tex
Added minor footnote describing Figure 1.

Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
average, and $\alpha$ is the power-law index describing the dependence of average satellite 
number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos 
by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly 
compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
grows with halo mass.

>>>>

Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
analyses. Look for the purple banana \footnote{'til they put us in the truck.} in the upper-left panel of 
Fig.~\ref{fig:Mr20triangle}. This panel illustrates that the 
parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
average, and $\alpha$ is the power-law index describing the dependence of average satellite 
number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos 
by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly 
compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
grows with halo mass.
